Clustering time series based on probability distributions across temporal granularities

### 2021-11-18 main.Rmd
fix position of WPD summary plot

```{r summary-plot-wpd, fig.cap = "fill this up", fig.height=6}
```

@@

>>>>

@@

```{r summary-plot-wpd, fig.cap = "Summary plots for three (a) and five (b) clusters from WPD showing the $wpd$ values of each customers across $hod$, $moy$, and $wnwd$ through a parallel coordinate plot. Group P-1 and P-2 correspond to Q-1 and Q-2 respectively. Cluster P-3 splits into Q-3, Q-4 and Q-5. ", fig.height=6}
```
